%-------------------------
% Resume in Latex
% Author : Ahmad Luqman
% License : MIT
%------------------------

\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[unicode=true,
              colorlinks=true,
              urlcolor=blue]{hyperref}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[4]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder 
#3 \lineunder
#4
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 $\bullet$  Selected Coursework:\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{Ahmad Luqman}
{Software Architect | DevOps and Lean practitioner | Kubernetes | Azure | Terraform | React | .Net | Mentor}
{I am a DevOps architect with passion of building great products by building culture of continuous improvement in people, process and products to enable continuous delivery of values to end users. I have almost 2 decades of experience engineering softwares on platforms varying from desktop, mobile, IOT and cloud and different operating systems. I have also contributed to .Net Core CLI and member of .Net foundation}
{+92-300-5560154 $\bullet$ ahmad.luqman@gmail.com  $\bullet$\url{http://www.linkedin.com/in/ahmadluqman} $\bullet$\url{https://github.com/ahmad-luqman} $\bullet$\url{https://https://twitter.com/ahmad_luqman}}

\header{Education}

\schoolwithcourses{GIK Institute}{Topi, Pakistan}{Bachelor of Science in Computer Systems Engineering, 2003}
{}
	\area{Computer Science}{ Unix Programming $\cdot$ Data Structures $\cdot$ Automata \& Computation $\cdot$ Computer System Fundamentals $\cdot$ Computer Networks $\cdot$ Operating Systems $\cdot$
 Algorithms $\cdot$ Object Oriented Systems $\cdot$ Image Processing $\cdot$
Artificial Intelligence $\cdot$ Databases}
	\area{Mathematics}{Calculus $\cdot$ Differential Equations $\cdot$ Discrete Mathematics $\cdot$ Numerical Analysis}
\schoolwithcourses{MOOC Courses}{Udacity,Edx,Coursera}{2013 - To date}
{}
	\area{\href{https://www.class-central.com/mooc/305/coursera-software-as-a-service}{Software Engineering for Software as a Service}}{ $\cdot$ Ruby on Rails Heroku Agile Development}
	\area{\href{https://www.edx.org/course/uc-berkeleyx/uc-berkeleyx-cs-184-1x-foundations-1003}{CS184.1x Foundation of Computer Graphics} - Nov 2013}{ OpenGL C++}
	\area{\href{https://www.coursera.org/course/startup}{Startup Engineering} - June 2013}{ HTML CSS Javascript NodeJs on AWS}
	\area{\href{https://www.coursera.org/course/datasci}{Introduction to Data Science} - June 2013}{SQL NoSQL Map Reduce Machine Learning}
	\area{\href{https://class.coursera.org/hetero-002}{MITx: 15.390x Entrepreneurship 101: Who is your customer?} - May 2014}{}
	\area{\href{https://www.class-central.com/course/coursera-algorithms-design-and-analysis-part-1-374}{Stanford University - Algorithms: Design and Analysis, Part 1} - July 2014}{}
	\area{\href{https://www.udacity.com/course/react-nanodegree--nd019}{React Nanodegree program} - May 2019}{ React Redux ReactNative}

\header{Work History}
\employer{LMKR}{March 2011 - To date}{Development Lead Platform, R\&D}
	\begin{achievements}
	\item Leading a Architecture and Configuration Management team responsible for setting up CI and daily builds and making desktop installers available to the respective teams.
	\item Job responsibilities include developing and architecting application, mentoring developers, doing code reviews, conducting technical interviews for hiring. 
	\item Currently working with 3d visualisation team maintaining and developing a product using C\#, WPF, SlimDX, DirectX 11 technologies.
	\item Contributed towards LMKR SDK for accessing Geographix database for well survey data using C\# and EF 5.0 and also helped in Well Planner application integration with smartSECTION
	\item Worked with Geology team and developing \& maintaining their products used for Oil \& Gas geological log interpretation workflows, improved performance of applications by parallelising User Defined Equations calculation for \href{http://www.lmkr.com/geographix/by-solution/geographix-suite/prizm%E2%84%A2/}{PRIZM\textsuperscript{TM}} using C++ PPL 
	\item Developed a XS2SS file format convertor utility in C\#, WPF with MVVM architecture and more than 80\% code coverage through unit tests.
	\item Worked on Volume Attributes team, a geophysical attributes calculator for seismic data interpretation in C\# 4.0 utilising TPL to parallelize processing. Also developed the UI in WPF.  
	\end{achievements}

\employer{Bentley Systems, inc. (Trivor Software was acquired by Bentley Systems, inc. in May 2007.)}{May 2007 - Feb 2011}{Senior Software Engineer/Team Lead}
	\begin{achievements}
	\item Worked on AutoPlant Core team and developed an offline ProjectWise (Bentley DMS product) project support for AutoPlant projects using C++/VB for legacy code and .Net C\# for newer modules. This was part of a Bentley AutoPlant XM 8.9.4 release. (March 2007 – August 2007)
	\item Worked on Platform Technology development group developing core Engineering Content Framework (ECFramework) used across multiple Bentley products being developed in .Net C\# and Windows Forms and contributed towards one major and two minor releases of V8i. (September 2007 - Feb 2011)
	\item Developed \& maintained Bentley Class Editor (Schema editing tool) for defining and editing schemas used across different applications across all Bentley verticals.
	\item Designed \& developed Engineering Units, ECSchema localization \& ECSchema Evolution for the ECFramework.
	\item Worked as a scrum master of one of team
	\item Introduced Software Engineering Line Engineering concept in the organisation
	\end{achievements}

\employer{Trivor Software(Exclusive Contractors for Bentley Systems, inc.)}{May 2005 - May 2007}{MIS Manager}
	\begin{achievements}
	\item Worked as a MIS Manager (Manager Management of Information Systems) in Trivor Software for six months.  
	\item Worked as a Software Engineer and successfully completed and developed an Engineering based project ‘BC PumpPlots’ for Brown and Caldwell. BC PumpPlots is an analysis tool for designing Pumping stations. (May 2005 – Feb 2007) 
	\end{achievements}

\clearpage

\employer{LMKR, IT Services}{May 2004 - April 2005}{System Administrator}
	\begin{achievements}
	\item Responsibility includes management of different services on Linux and Windows environment.
	\item Common tasks include management of Active Directory, FTP, RAS, DHCP, Citrix Server, squid proxy, DNS and backup of servers.
	\item Worked on the design and implementation of the new services like GPOs, SMS, SFU, DHCP and DFS. 
	\item Also worked on documenting the policies and procedures of the department for ISO-9000 Certification. 
	\end{achievements}

\employer{GIK Institute, Faculty of Electronic Engineering, Topi}{May 2003 - May 2004}{Electronic Engineer}
	\begin{achievements}
	\item Assisted Image processing course, Conducted labs for Digital logic design, Computer networks and Image processing courses.
	\item Developed an application in C++ for reading data from a centrifugal machine in Materials Engineering Faculty’s lab from its COM Serial port and saving it in .csv file so that data could be plotted in Microsoft Excel.
	\item As a system administrator was responsible for maintaining the network of the faculty and computer labs.
	\item Assisted a graduate student in his thesis work for developing linux kernel modules for system call based anomaly intrusion detection system
	\end{achievements}

\employer{Advanced Engineering Research Organisation}{summer 2001/2002}{Internee}
	\begin{achievements}
	\item Worked on video tracking system project using C++ and OpenGL 1.1 and was continued as a final year project for bachelors degree
	\item Configured a redhat based linux server running sendmail, squid based proxy and software router
	\item Developed and ported a framework for secure VOIP solution to PC on which different encryption protocols and audio encoding protocols could be tested.
	\end{achievements}

\header{Skills}
\begin{achievements}
\item Proficiency in Kubernetes, Dockers, Azure, Terraform, Vagrant
\item Managing development teams using GitHub, GitLab, Azure Devops, TFS
\item Proficiency in C\#, C/C++
\item Windows Form, WPF, MVVM, TDD, Unit Tests, React
\item Java, VB.Net, PL/SQL, Python, Javascript, Typescript
\item DirectX 11, HLSL, OpenGL
\item Regular Expressions, Threads, Sockets, SQL, \LaTeX
\end{achievements}

\end{document}
